---
title: "Air Pollutant Spatial Interpolation"
output: html_notebook
---

# Library Loading
```{r, warning=FALSE, verbose=FALSE, message=FALSE}
library(tidyverse)
library(lubridate)
library(tidyr)
library(sf)
library(rgdal)
library(sp)
library(gstat)
library(raster)
library(ggplot2)
library(leaflet)
library(tmap)
library(geojsonio)
library(geojsonlint)
library(lattice)
library(gridExtra)
```

# Reading AQI Data
```{r, verbose=FALSE, warning=FALSE, message=FALSE}
# Reading AQI Data GeoJSON
AQI <- readOGR("Data/2019AnnualConc/2019AnnualConc.geojson")
States <- readOGR("Data/StateMerged/StateMerged.geojson")
```

```{r}
categories_to_keep <- c("Ozone", "Nitrogen dioxide (NO2)", "PM2.5 - Local Conditions")
AQI_filtered <- AQI[AQI$Parameter1 %in% categories_to_keep,]

ozone_data <- AQI_filtered[AQI_filtered$Parameter1 == "Ozone",]
no2_data <- AQI_filtered[AQI_filtered$Parameter1 == "Nitrogen dioxide (NO2)",]
pm25_data <- AQI_filtered[AQI_filtered$Parameter1 == "PM2.5 - Local Conditions",]

ozone_data_unique <- ozone_data[!duplicated(ozone_data@data[c("Latitude", "Longitude")]),]
no2_data_unique <- no2_data[!duplicated(no2_data@data[c("Latitude", "Longitude")]),]
pm25_data_unique <- pm25_data[!duplicated(pm25_data@data[c("Latitude", "Longitude")]),]
```

```{r}
# Ozone Concentration Summary Statistics
ozone_summary <- ozone_data_unique@data$Arithmetic %>%
  summary()
# NO2 Concentration Summary Statistics
no2_summary <- no2_data_unique@data$Arithmetic %>%
  summary()
# PM 2.5 Concentration Summary Statistics
pm25_summary <- pm25_data_unique@data$Arithmetic %>%
  summary()

ozone_summary; no2_summary; pm25_summary

# Histograms of Air Pollutant Concentrations
par(mfrow=c(1,3))
hist(ozone_data_unique@data$Arithmetic, main="Ozone Concentration",
     xlab = "Ozone Concentration Value (ppm)")
hist(no2_data_unique@data$Arithmetic, main="Nitrogen dioxide Concentration",
     xlab = "Nitrogen dioxide Concentration (ppm)")
hist(pm25_data_unique@data$Arithmetic, main="PM 2.5 Concentration",
     xlab = "PM 2.5 Concentration (μg/mᶟ)")
```

# Checking Projection
```{r}
proj4string(ozone_data_unique)
proj4string(no2_data_unique)
proj4string(pm25_data_unique)
```
# Counting Measurement Stations
```{r}
ozone_station_count <- ozone_data_unique@data %>%
  distinct(Latitude, Longitude, .keep_all = TRUE) %>%
  group_by(Latitude, Longitude) %>%
  summarise(num_stations = n())

nrow(ozone_station_count) #159 stations

no2_station_count <- no2_data_unique@data %>%
  distinct(Latitude, Longitude, .keep_all = TRUE) %>%
  group_by(Latitude, Longitude) %>%
  summarise(num_stations = n())

nrow(no2_station_count) #79 stations

pm25_station_count <- pm25_data_unique@data %>%
  distinct(Latitude, Longitude, .keep_all = TRUE) %>%
  group_by(Latitude, Longitude) %>%
  summarise(num_stations = n())

nrow(pm25_station_count) #94 stations

```


# IDW Spatial Interpolation - Location Plot with Points to be Predicted
```{r}
n_points <- 100
predictions <- spsample(States, n_points, "random")

par(mfrow=c(1,3))
plot(ozone_data_unique)
plot(predictions, add=TRUE, col = "RED")
plot(no2_data_unique)
plot(predictions, add=TRUE, col = "RED")
plot(pm25_data_unique)
plot(predictions, add=TRUE, col = "RED")
```
# IDW Spatial Interpolation - IDW Predicted Plots
```{r}
Ozonepred <- idw(Arithmetic ~ 1,
            ozone_data_unique,
            predictions,
            idp = 2)

NO2pred <- idw(Arithmetic ~ 1,
            no2_data_unique,
            predictions,
            idp = 2)

PM25pred <- idw(Arithmetic ~ 1,
            pm25_data_unique,
            predictions,
            idp = 2)

par(mfrow=c(1,3))
SamplePlot1 <- spplot(Ozonepred, "var1.pred", main = "Ozone Pred. (k=2, n=100)",
                      sp.layout = list(polygons(States)))
SamplePlot2 <- spplot(NO2pred, "var1.pred", main = "NO2 Pred. (k=2, n=100)",
                      sp.layout = list(polygons(States)))
SamplePlot3 <- spplot(PM25pred, "var1.pred", main = "PM2.5 Pred. (k=2, n=100)",
                      sp.layout = list(polygons(States)))

grid.arrange(SamplePlot1, SamplePlot2, SamplePlot3, ncol = 3)
```

# Cross Validation
```{r}
LOOCV_Ozone <- krige.cv(Arithmetic ~ 1,
                        ozone_data_unique,
                        nfold = nrow(ozone_data_unique),
                        set = list(idp = 2))

LOOCV_Ozone@data

LOOCV_NO2 <- krige.cv(Arithmetic ~ 1,
                      no2_data_unique,
                      nfold = nrow(no2_data_unique),
                      set = list(idp = 2))

LOOCV_NO2@data

LOOCV_PM25 <- krige.cv(Arithmetic ~ 1,
                       pm25_data_unique,
                       nfold = nrow(pm25_data_unique),
                       set = list(idp = 2))

LOOCV_PM25@data
```

# LOOCV Residual Plot
```{r}
loocvOzonePlot <- spplot(LOOCV_Ozone, "residual", main="Ozone Resid (k=2, n=100)",
                         sp.layout = list(polygons(States)))
loocvNO2Plot <- spplot(LOOCV_NO2, "residual", main="NO2 Resid (k=2, n=100)",
                       sp.layout = list(polygons(States)))
loocvPM25Plot <- spplot(LOOCV_PM25, "residual", main="PM2.5 Resid (k=2, n=100)",
                        sp.layout = list(polygons(States)))
grid.arrange(loocvOzonePlot, loocvNO2Plot, loocvPM25Plot, ncol = 3)
```

# Measurement of Fit
```{r}
# RMSE of Air Pollutant LOOCV

RMSE_resid <- function(x){
  return(sqrt(mean(x^2)))
}

RMSE_resid(LOOCV_Ozone@data$residual) # RMSE.ozone: 0.003207004
RMSE_resid(LOOCV_NO2@data$residual) # RMSE.no2: 7.546449
RMSE_resid(LOOCV_PM25@data$residual) # RMSE.pm25: 1.703405

# Generally, RMSE of Residuals lower than 1 indicates good agreement so 
# the parameter k of NO2 has to be adjusted 
```

# Refitting with new exponent parameter k for IDW (k=3)
```{r}
# NO2.idw <- idw(Arithmetic ~ 1,no2_data_unique, predictions, idp=3)

LOOCV_NO2_k3 <- krige.cv(Arithmetic ~ 1,
                      no2_data_unique,
                      nfold = nrow(no2_data_unique),
                      set = list(idp = 3))

LOOCV_NO2_k3@data

LOOCV_PM25_k3 <- krige.cv(Arithmetic ~ 1,
                       pm25_data_unique,
                       nfold = nrow(pm25_data_unique),
                       set = list(idp = 3))

LOOCV_PM25_k3@data

RMSE_resid(LOOCV_NO2_k3@data$residual) # RMSE.no2: 7.902865 (increased RMSE)
RMSE_resid(LOOCV_PM25_k3@data$residual) # RMSE.pm25: 1.797648 (increased RMSE)
```

# Refitting with new exponent parameter k for IDW (k=1.5)
```{r}
LOOCV_NO2_k15 <- krige.cv(Arithmetic ~ 1,
                      no2_data_unique,
                      nfold = nrow(no2_data_unique),
                      set = list(idp = 1.5))

LOOCV_NO2_k15@data

LOOCV_PM25_k15 <- krige.cv(Arithmetic ~ 1,
                       pm25_data_unique,
                       nfold = nrow(pm25_data_unique),
                       set = list(idp = 1.5))

LOOCV_PM25_k15@data

RMSE_resid(LOOCV_NO2_k15@data$residual) # RMSE.no2: 7.356047 (decreased RMSE)
RMSE_resid(LOOCV_PM25_k15@data$residual) # RMSE.pm25: 1.668088 (decreased RMSE)
```

# Refitting with new exponent parameter k for IDW (k=0.5)
```{r}
LOOCV_NO2_k.5 <- krige.cv(Arithmetic ~ 1,
                      no2_data_unique,
                      nfold = nrow(no2_data_unique),
                      set = list(idp = 0.5))

LOOCV_NO2_k15@data

LOOCV_PM25_k.5 <- krige.cv(Arithmetic ~ 1,
                       pm25_data_unique,
                       nfold = nrow(pm25_data_unique),
                       set = list(idp = 0.5))

LOOCV_PM25_k.5@data

RMSE_resid(LOOCV_NO2_k.5@data$residual) # RMSE.no2: 10.15379 (increased RMSE)
RMSE_resid(LOOCV_PM25_k.5@data$residual) # RMSE.pm25: 1.876017 (increased RMSE)
```

# Refitting with new exponent parameter k for IDW (k=1)
```{r}
LOOCV_NO2_k1 <- krige.cv(Arithmetic ~ 1,
                      no2_data_unique,
                      nfold = nrow(no2_data_unique),
                      set = list(idp = 1))

LOOCV_NO2_k1@data

LOOCV_PM25_k1 <- krige.cv(Arithmetic ~ 1,
                       pm25_data_unique,
                       nfold = nrow(pm25_data_unique),
                       set = list(idp = 1))

LOOCV_PM25_k1@data

RMSE_resid(LOOCV_NO2_k1@data$residual) # RMSE.no2: 7.356047 (increased RMSE)
RMSE_resid(LOOCV_PM25_k1@data$residual) # RMSE.pm25: 1.668088 (increased RMSE)
```

# Loop for parameter k
```{r}
# Looping parameter k LOOCV for Ozone Concentration Data IDW
RMSE_values_ozone <- c()
k_values <- seq(0, 5, by = 0.1)
for (k in k_values) {
  RMSE_values_ozone <- c(RMSE_values_ozone, RMSE_resid(krige.cv(Arithmetic ~ 1,
                                                    ozone_data_unique,
                                                    nfold = nrow(ozone_data_unique),
                                                    set = list(idp = k))@data$residual))
}
plot(k_values, RMSE_values_ozone, type = "o", xlab = "k", ylab = "RMSE (for Ozone data)")

min_RMSE_ozone <- min(RMSE_values_ozone)
min_k_ozone <- k_values[which.min(RMSE_values_ozone)]
text(min_k_ozone, min_RMSE_ozone,
     paste0("k = ", min_k_ozone, "\nRMSE = ", round(min_RMSE_ozone, 2)), pos = 4, cex=0.5)



# Looping parameter k LOOCV for NO2 Concentration Data IDW
RMSE_values_no2 <- c()
k_values <- seq(0, 5, by = 0.1)
for (k in k_values) {
  RMSE_values_no2 <- c(RMSE_values_no2, RMSE_resid(krige.cv(Arithmetic ~ 1,
                                                    no2_data_unique,
                                                    nfold = nrow(no2_data_unique),
                                                    set = list(idp = k))@data$residual))
}
plot(k_values, RMSE_values_no2, type = "o", xlab = "k", ylab = "RMSE (for NO2 data)")

min_RMSE_no2 <- min(RMSE_values_no2)
min_k_no2 <- k_values[which.min(RMSE_values_no2)]
text(min_k_no2, min_RMSE_no2,
     paste0("k = ", min_k_no2, "\nRMSE = ", round(min_RMSE_no2, 2)), pos = 4, cex=0.5)


# Looping parameter k LOOCV for PM2.5 Concentration Data IDW
RMSE_values_pm25 <- c()
k_values <- seq(0, 5, by = 0.1)
for (k in k_values) {
  RMSE_values_pm25 <- c(RMSE_values_pm25, RMSE_resid(krige.cv(Arithmetic ~ 1,
                                                    pm25_data_unique,
                                                    nfold = nrow(pm25_data_unique),
                                                    set = list(idp = k))@data$residual))
}
plot(k_values, RMSE_values_pm25, type = "o", xlab = "k", ylab = "RMSE (for PM 2.5 data)")

min_RMSE_pm25 <- min(RMSE_values_pm25)
min_k_pm25 <- k_values[which.min(RMSE_values_pm25)]
text(min_k_pm25, min_RMSE_pm25, 
     paste0("k = ", min_k_pm25, "\nRMSE = ", round(min_RMSE_pm25, 2)), pos = 4, cex=0.5)
```

# IDW Model Parameter Selection for Each Pollutant
```{r}
# Ozone IDW Model Parameter and RMSE
print(min_k_ozone)  # k = 1
print(min_RMSE_ozone) # RMSE: 0.003045932

# NO2 IDW Model Parameter and RMSE
print(min_k_no2) # k = 1.3
print(min_RMSE_no2) # RMSE: 7.326283

# PM2.5 IDW Model Parameter and RMSE
print(min_k_pm25) # k = 1.3
print(min_RMSE_pm25) # RMSE: 1.665076
```
# IDW Spatially Interpolated Raster Map for Each Pollutant
```{r}
# Ozone dataset
ozone_data_unique@data

# NO2 dataset
no2_data_unique@data

# PM2.5 dataset
pm25_data_unique@data

k_ozone <- 1
k_no2 <- 1.3
k_pm25 <- 1.3
```

```{r}
ozone_coords <- ozone_data_unique[, c("Longitude", "Latitude")]
no2_coords <- no2_data_unique[, c("Longitude", "Latitude")]
pm25_coords <- pm25_data_unique[, c("Longitude", "Latitude")]

# Check for duplicated coordinates
duplicated(ozone_coords@data)
duplicated(no2_coords@data)
duplicated(pm25_coords@data)
```

```{r}
SampPoints <- spsample(x = States, n = 40000, type = "random")

IDW_Ozone = gstat::idw(formula = Arithmetic ~ 1,
                       locations = ozone_data_unique,
                       newdata = SampPoints ,
                       idp = 1)

IDW_NO2 = gstat::idw(formula = Arithmetic ~ 1,
                     locations = no2_data_unique,
                     newdata = SampPoints ,
                     idp = 1.3)

IDW_PM25 = gstat::idw(formula = Arithmetic ~ 1,
                      locations = pm25_data_unique,
                      newdata = SampPoints,
                      idp = 1.3)


tmapOzone = tm_shape(IDW_Ozone) + 
  tm_dots(col = "var1.pred", size = 0.05, title = "Predicted Concentration") + 
  tm_shape(States) + 
  tm_borders(col = "black", lwd=2) +
  tm_layout(main.title = "IDW Spatial Interpolated 2019 Ozone Concentration",
            main.title.position = "center",
            legend.position = c("center","bottom"),
            legend.outside = TRUE)

tmapNO2 = tm_shape(IDW_NO2) + 
  tm_dots(col = "var1.pred", size = 0.05, title = "Predicted Concentration") +
  tm_shape(States) + 
  tm_borders(col = "black", lwd=2) + 
  tm_layout(main.title = "IDW Spatial Interpolated 2019 NO2 Concentration",
            main.title.position = "center",
            legend.position = c("center","bottom"),
            legend.outside = TRUE)

tmapPM25 = tm_shape(IDW_PM25) + 
  tm_dots(col = "var1.pred", size = 0.05, title = "Predicted Concentration") +
  tm_shape(States) + 
  tm_borders(col = "black", lwd=2) + 
  tm_layout(main.title = "IDW Spatial Interpolated 2019 PM 2.5 Concentration",
            main.title.position = "center",
            legend.position = c("center","bottom"),
            legend.outside = TRUE)

par(mfrow=c(1,3))
tmapOzone; tmapNO2; tmapPM25
```

# Exporting the Data Cleaned Air Pollutants as GeoJSON for Clustering (in GeoDa)
```{r}
Ozone_States <- SpatialPolygonsDataFrame(States, data = data.frame(ozone_data_unique@data, row.names = row.names(ozone_data_unique)))
NO2_States <- SpatialPolygonsDataFrame(States, data = data.frame(no2_data_unique@data, row.names = row.names(no2_data_unique)))
PM25_States <- SpatialPolygonsDataFrame(States, data = data.frame(pm25_data_unique@data, row.names = row.names(pm25_data_unique)))

OzoneGJ <- geojson_json(Ozone_States)
NO2GJ <- geojson_json(NO2_States)
PM25GJ <- geojson_json(PM25_States)

write(OzoneGJ, file = "OzoneGJ.geojson")
write(NO2GJ, file = "NO2GJ.geojson")
write(PM25GJ, file = "PM25GJ.geojson")

OzoneIDWGJ <- geojson_json(IDW_Ozone)
write(OzoneIDWGJ, file = "OzoneIDWGJ.geojson")
```

# Air Pollutant Concentration over Longitude and Latitude grid
```{r}
ggplot(data = ozone_data_unique@data)+
  geom_point(mapping = aes(x = Longitude, y = Latitude, size = Arithmetic),
             color = "brown", alpha = 3/4) +
  ggtitle("Ozone Concentration (ppm)") +
  coord_fixed()

ggplot(data = no2_data_unique@data)+
  geom_point(mapping = aes(x = Longitude, y = Latitude, size = Arithmetic),
             color = "purple", alpha = 3/4) +
  ggtitle("Nitrogen dioxide Concentration (ppm)") +
  coord_fixed()

ggplot(data = pm25_data_unique@data)+
  geom_point(mapping = aes(x = Longitude, y = Latitude, size = Arithmetic),
             color = "navy", alpha = 3/4) +
  ggtitle("PM2.5 Concentration (μg/mᶟ)") +
  coord_fixed()
```

# Bounding Box
```{r}
bbox(ozone_data_unique)
bbox(no2_data_unique)
bbox(pm25_data_unique)
```

# Normality Assumption Checking 
```{r}
par(mfrow=c(1,3))
hist(ozone_data_unique@data$Arithmetic, main="Ozone Concentration",
     xlab = "Ozone Concentration Value (ppm)")
hist(no2_data_unique@data$Arithmetic, main="Nitrogen dioxide Concentration",
     xlab = "Nitrogen dioxide Concentration (ppm)")
hist(pm25_data_unique@data$Arithmetic, main="PM 2.5 Concentration",
     xlab = "PM 2.5 Concentration (μg/mᶟ)")
```
# Log-transformation of Air Pollutant Data
```{r}
# Log-transformation of Ozone Concentration Data
ozone_data_unique@data$logArith <- log(ozone_data_unique@data$Arithmetic)

# Log-transformation of Nitrogen dioxide Concentration Data
no2_data_unique@data$logArith <- log(no2_data_unique@data$Arithmetic)

# Histogram of Air Pollutant Concentration after necessary Log-transformation
par(mfrow=c(1,3))
hist(ozone_data_unique@data$logArith, main="Log(Ozone Concentration)",
     xlab = "Log(Ozone Concentration)", cex.main = 1)
hist(no2_data_unique@data$logArith, main="Log(Nitrogen dioxide Concentration)",
     xlab = "Log(Nitrogen dioxide Concentration)", cex.main = 1)
hist(pm25_data_unique@data$Arithmetic, main="PM 2.5 Concentration",
     xlab = "PM 2.5 Concentration (μg/mᶟ)")

# All passes Normality Assumption
```
# Calculating Sample (Empirical) Variogram 
```{r}
# Ozone Concentration Sample Variogram
ozone.vgm <- variogram(logArith ~ 1, ozone_data_unique)

# NO2 Concentration Sample Variogram
no2.vgm <- variogram(logArith ~ 1, no2_data_unique)

# PM 2.5 Concentration Sample Variogram
pm25.vgm <- variogram(Arithmetic ~ 1, pm25_data_unique)

plot(ozone.vgm, main = "Sample Variogram of Log (Ozone Concentration)")
plot(no2.vgm, main = "Sample Variogram of Log(NO2 Concentration)")
plot(pm25.vgm, main = "Sample Variogram of PM 2.5 Concentration")


```

# List of Possible Variogram Models
```{r}
show.vgms()

# List of semivariance value 
SampleOzoneSemiVar <- ozone.vgm$gamma
SampleNO2SemiVar <- no2.vgm$gamma
SamplePM25SemiVar <- pm25.vgm$gamma

print("-----------Ozone Semivariance----------")
print(SampleOzoneSemiVar)
print("------------NO2 Semivaraince-----------")
print(SampleNO2SemiVar)
print("----------PM 2.5 Semivariance----------")
print(SamplePM25SemiVar)

# Sample Ozone Variogram would fit for "Nug" or "Per" or "Hol"
# Sample NO2 Variogram would fit for "Gau"
# Sample PM 2.5 Variogram would fit for "Wav" or "Per"
```

# Fitting Possible Variograms
```{r}
# Ozone Variogram of "Per", "Hol"
ozonePer.fit <- fit.variogram(ozone.vgm, model = vgm("Per"))
ozoneHol.fit <- fit.variogram(ozone.vgm, model = vgm("Hol"))

# NO2 Variogram of "Per", "Gau"
no2Per.fit <- fit.variogram(no2.vgm, model = vgm("Per"))
no2Gau.fit <- fit.variogram(no2.vgm, model = vgm("Gau"))

# PM 2.5 Variogram of "Per", "Wav"
pm25Per.fit <- fit.variogram(pm25.vgm, model = vgm("Per"))
pm25Wav.fit <- fit.variogram(pm25.vgm, model = vgm("Wav"))
```

# Plotting each Possible Fit
```{r}
# Ozone Possible Variogram Fit Plot
plot(ozone.vgm, ozonePer.fit, main = "Ozone (Per)")
plot(ozone.vgm, ozoneHol.fit, main = "Ozone (Hol)") # Best represents

# NO2 Possible Variogram Fit Plot
plot(no2.vgm, no2Per.fit, main = "NO2 (Per)")
plot(no2.vgm, no2Gau.fit, main = "NO2 (Gau)") # Best represents

# PM 2.5 Possible Variogram Fit Plot
plot(pm25.vgm, pm25Per.fit, main = "PM 2.5 (Per)")
plot(pm25.vgm, pm25Wav.fit, main = "PM 2.5 (Wav)") # Best represents
```

# Model Parameter Specifications
```{r}
# vgm(0.001009458, "Hol", 158.1515)
ozoneHol.fit # psill: 0.001009458	, range: 158.1515	 

# vgm(0.7650246, "Gau",104.2188)
no2Gau.fit # psill: 0.7650246	, range: 104.2188	

# vgm(3.000621, "Wav", 213.0957)
pm25Wav.fit # psill: 3.000621 , range: 213.0957

LOOCV_krige_ozone <- krige.cv(logArith ~ 1, 
                        ozone_data_unique, 
                        model = ozoneHol.fit)

LOOCV_krige_no2 <- krige.cv(logArith ~ 1, 
                        no2_data_unique, 
                        model = no2Gau.fit)

LOOCV_krige_pm25 <- krige.cv(Arithmetic ~ 1, 
                        pm25_data_unique, 
                        model = pm25Wav.fit)

LOOCVKrigOzoneResid <- LOOCV_krige_ozone@data$residual
LOOCVKrigNO2Resid <- LOOCV_krige_no2@data$residual
LOOCVKrigPM25Resid <-LOOCV_krige_pm25@data$residual

RMSE_resid(LOOCVKrigOzoneResid)
RMSE_resid(LOOCVKrigNO2Resid)
RMSE_resid(LOOCVKrigPM25Resid)

options(scipen=999)
attr(ozoneHol.fit, "SSErr")
attr(no2Gau.fit, "SSErr")
attr(pm25Wav.fit, "SSErr")
```

# Creating a convex hull
```{r}
# Row IDs of points for convex hull
convex_hull_point_ids_ozone <- ozone_data_unique@coords %>%
  chull()

convex_hull_point_ids_no2 <- no2_data_unique@coords %>%
  chull()

convex_hull_point_ids_pm25 <- pm25_data_unique@coords %>%
  chull()

# Sub-setting the points for convex hull and convert to data frame
convex_hull_points_ozone <- ozone_data_unique@coords[convex_hull_point_ids_ozone,] %>%
  as.data.frame()

convex_hull_points_no2 <- no2_data_unique@coords[convex_hull_point_ids_no2,] %>%
  as.data.frame()

convex_hull_points_pm25 <- pm25_data_unique@coords[convex_hull_point_ids_pm25,] %>%
  as.data.frame()

# Plotting convex hull points for each air pollutant
plot(convex_hull_points_ozone)
plot(convex_hull_point_ids_no2)
plot(convex_hull_point_ids_pm25)
```

# Creating a Polygon from the Convex Hull Points
```{r}
# Creating a matrix of the convex hull point coordinates
coordsOzone <- coordinates(convex_hull_points_ozone)
coordsNO2 <- coordinates(convex_hull_points_no2)
coordsPM25 <- coordinates(convex_hull_points_pm25)

# Creating a Polygon
polyOzone <- sp::Polygon(coordsOzone)
polyNO2 <- sp::Polygon(coordsNO2)
polyPM25 <- sp:: Polygon(coordsPM25)

# Preparing data for a "sp" object
ID <- "Minimum Boundary"
PlsOzone <- Polygons(list(polyOzone), ID = ID)
PlsNO2 <- Polygons(list(polyNO2), ID = ID)
PlsPM25 <- Polygons(list(polyPM25), ID = ID)

SPlsOzone <- SpatialPolygons(list(PlsOzone))
SPlsNO2 <-SpatialPolygons(list(PlsNO2))
SPlsPM25 <- SpatialPolygons(list(PlsPM25))

plot(SPlsOzone)
plot(SPlsNO2)
plot(SPlsPM25)
```

# Creating evenly spaced grid
```{r}
gridOzone <- makegrid(SPlsOzone, cellsize = 0.1)
gridNO2 <- makegrid(SPlsNO2, cellsize = 0.1)
gridPM25 <- makegrid(SPlsPM25, cellsize = 0.1)

coordinates(gridOzone) <- ~ x1+x2
coordinates(gridNO2) <- ~ x1+x2
coordinates(gridPM25) <- ~ x1+x2

plot(gridOzone)
plot(gridNO2)
plot(gridPM25)
```

# Selecting only grid points within convex hull
```{r}
# Checking which grid cells are in the polygon
grid_in_poly_ozone <- sp::over(gridOzone, SPlsOzone)
grid_in_poly_no2 <- sp::over(gridNO2, SPlsNO2)
grid_in_poly_pm25 <- sp::over(gridPM25, SPlsPM25)

# List of NAs and valid grid cells
grid_in_poly_ozone
grid_in_poly_no2
grid_in_poly_pm25

# Selecting only points that are not NA 
grid_predict_ozone <- gridOzone[!is.na(grid_in_poly_ozone),]
grid_predict_no2 <- gridNO2[!is.na(grid_in_poly_no2),]
grid_predict_pm25 <- gridPM25[!is.na(grid_in_poly_pm25),]

# Plotting
plot(grid_predict_ozone)
plot(grid_predict_no2)
plot(grid_predict_pm25)
```

# Predicting Air Pollutant Concentration Values at New Points 
```{r}
# Setting CRS of grid_predict's of every air pollutants to the spatial data set
crs(grid_predict_ozone) <- CRS("+proj=longlat +datum=WGS84 +no_defs")
crs(grid_predict_no2) <- CRS("+proj=longlat +datum=WGS84 +no_defs")
crs(grid_predict_pm25) <- CRS("+proj=longlat +datum=WGS84 +no_defs")

# Kriging of Ozone Concentration over Grid Cells
ozone_krige <- krige(log(Arithmetic) ~ 1,
                        ozone_data_unique,
                        grid_predict_ozone,
                        model = ozoneHol.fit)

# Kriging of NO2 Concentration over Grid Cells
no2_krige <- krige(log(Arithmetic) ~ 1,
                        no2_data_unique,
                        grid_predict_no2,
                        model = no2Gau.fit)

# Kriging of PM 2.5 Concentration over Grid Cells
pm25_krige <- krige(Arithmetic ~ 1,
                        pm25_data_unique,
                        grid_predict_pm25,
                        model = pm25Wav.fit)
```

# Plotting Air Pollutant Concentration Predictions
```{r}
# Exponential-transformation of Log(Ozone) back to original scale
ozone_krige_copy <- ozone_krige
ozone_krige_copy@data$Pred <- exp(ozone_krige@data$var1.pred)

# Exponential-transformation of Log(NO2) back to original scale
no2_krige_copy <- no2_krige
no2_krige_copy@data$Pred <- exp(no2_krige@data$var1.pred)

# Plotting the original scale of Kriging Prediction Air Pollutant Concentrations
KrigOzonePlot <- spplot(ozone_krige_copy, "Pred", main="Kriging of Ozone",
                         sp.layout = list(list(States, fill=alpha("white", 0.01), lwd=2, first=FALSE)))

KrigNO2Plot <- spplot(no2_krige_copy, "Pred", main = "Kriging of NO2",
                      sp.layout = list(list(States, fill=alpha("white", 0.01), lwd=2, first=FALSE)))

KrigPM25Plot <- spplot(pm25_krige, "var1.pred", main = "Kriging of PM 2.5",
                       sp.layout = list(list(States, fill=alpha("white", 0.01), lwd=2, first=FALSE)))
grid.arrange(KrigOzonePlot, KrigNO2Plot, KrigPM25Plot, ncol = 3)
```
